Make any stupid plot you want

### 2020-12-17 draft/sections/math.tex
artist?

The artist acts on a sheaf because some visual characterstics, such as line thickness, need more information than just the data at a point. The artist is the composition of visual variable mappers $F: E \rightarrow V$ and assembly function  $Q: V \rightarrow H$ that transforms $V$ into a visual idiom\cite{munznerMarksChannels} in pre-render space:

\begin{equation}
    \begin{tikzcd}
        O(E) \arrow[r, "F" description] \arrow[rd, "A"'] \arrow[rd] & O(V) \arrow[d, "Q" description] \\
                                                                    & O(H)                           
        \end{tikzcd}
\end{equation}

The mapping from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space

@@

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description]              & H \arrow[d, "\pi" description]                                    \\
        K \arrow[u, "\tau" description, bend right] & S \arrow[l, "\xi" description] \arrow[lu, "\xi^*\tau" description]
        \end{tikzcd}
\end{equation}
and can be pulled back up to $E$ (or $V$) such that for a region $s$ there is an associated record $\tau$ and visual mapping $\mu$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        V \arrow[r, "q" description]                                       & H \\
        S \arrow[u, "\xi^*\mu" description] \arrow[ru, "\rho" description] &  
    \end{tikzcd}
\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

\subsubsection{Channels}
\begin{equation}
    \begin{tikzcd}
        E_1 \arrow[r, "F" description] \arrow[d, "f" description] & V_1 \arrow[d, "f" description] \\
        E_2 \arrow[r, "F" description]                            & V_2                           
    \end{tikzcd}
\end{equation}

>>>>

The artist acts on a sheaf because some visual characterstics, such as line thickness, need more information than just the data at a point. The artist through $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space

@@

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description]              & H \arrow[d, "\pi" description]                                    \\
        K \arrow[u, "\tau" description, bend right] & S \arrow[l, "\xi" description] \arrow[lu, "\xi^*\tau" description]
        \end{tikzcd}
\end{equation}
and can be pulled back up to $E$ (or $V$) such that for a region $s$ there is an associated record $\tau$ and visual mapping $\mu$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}

\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

\subsubsection{Channels}
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nus$ is a functor from data to visual space such that any $\nu$ is an equivariant map if

\begin{equation}
    \begin{tikzcd}
        E_1 \arrow[r, "F" description] \arrow[d, "" description] & V_1 \arrow[d, "f" description] \\
        E_2 \arrow[r, "F" description]                            & V_2                           
    \end{tikzcd}
\end{equation}
